Improving Outcome Predictions for Patients Receiving Mechanical Circulatory Support by Optimizing Imputation of Missing Values

### 2020-11-10 doc_arXiv/response_to_reviewers.Rmd

__Response__: We agree and have added the following sentence to our paragraph on limitations in the revised manuscript: "The models we studied obtained low values of scaled Brier score, indicating low prediction accuracy. It is unclear how results may vary for models with higher prediction accuracy."

__Comment 7__: Table 2. please clarify when modeling mortality events, how patients with transplants events and cessation were used, are they treated as censoring or are they dropped? Please explain the potential bias if the transplant patients were not included into the analysis for mortality events. The same question for modeling transplant events, how dead and cessations were handled in the cox model for transplant risk?

__Response__: The reviewer has correctly identified that patients who received transplant or cessation of support were censored at the time of these events in mortality risk prediction models. Similarly, patients who died or received cessation of support were censored at the time of these events in transplant risk prediction models. We have clarified this approach in our "Outcomes and Predictors" section, where we write "For each outcome, we censored patients at the time of competing risks events. For example, in risk prediction models for mortality, patients who were lost to follow-up, received transplant, or had cessation of support were censored at the time of this event".

__Comment 8__: Table 3. The concordance is low, which indicates low model performance. The table title has a typo for "mortality".

__Response__: Thank you for catching this typo. We have changed 'morality' to 'mortality' and have taken steps to improve the discrimination of the risk prediction models in the current study. These steps are outlined in our response to __Comment 2__ above.

__Comment 9__: Page 15. Line 3. Based on Table 3, for GBDT, the improvement in scale Brier score from KNN (MI) is 0.7 compared to the reference strategy. For CIF, the improvement from KNN (MI) is 0.8 when compared to the reference. These are slightly off in the text, which could be rounding issues. Please clarify.

__Response:__ Thank you for noticing these inconsistencies due to rounding. We have corrected these typos and now use the same rounding specification throughout the manuscript.

__Comment 10__: Page 15 Line 6-8. From Table 3, for the CIF, stepwise PH and GBDT, the missing data strategies that provided the lowest calibration error were missForest, KNN (MI), and BR respectively. Please correct the order of the statement.

__Response__: Thank you for catching this typo. This sentence was deleted from the revised manuscript due to the substantial revisions applied to our analysis.
